---
title: "Final Project Preliminary Report"
author: "Shirley Song"
date: "`r Sys.Date()`"
knitr:
  opts_chunk:
    fig.align: center
    fig.height: 5
    fig.width: 7
    results: markup
---

```{r, set-chunk-opts, echo = FALSE}
library(knitr)
opts_chunk$set(
  echo = FALSE,  
  warning = FALSE, 
  message = FALSE
)
```

## Introduction

The dataset contains 369 unique patients with their scores of Patient Health Questionnaire-9 (PHQ-9) for depression screening and the seven question Generalized Anxiety Disorder-7 (GAD-7) mental illness screening survey documented. Both PHQ-9 and GAD-7 were collected with either a stereotype mobile apps or traditional method. Other variables like age group, gender, prior depression treatment, race, whether work remotely were also included.

We are aiming to explore the depression diagnosis cut-off point using PHQ-9 or GAD-7 total score and see which covariates have the strongest correlation to the the depression diagnosis.

## Tabular Analysis

The Table describe the overall distribution of PHQ-9 and GAD-7 score, as well as other covariates distribution, stratified by two data collection methods.

```{r}
readRDS(here::here("output", "tabular.rds"))
```

## Graphical Analysis

The graph show how total PHQ-9 and GAD-7 total score distributed and what should be the cut off point for Depression Diagnosis.

```{r}
readRDS(here::here("output", "graph.rds"))
```
